\documentclass[3p]{elsarticle}

\usepackage{tgpagella}
\usepackage{subcaption}

\usepackage{hyperref}
\hypersetup{
	colorlinks=true,
	linkcolor=blue,
	filecolor=magenta,      
	urlcolor=black,
}
\usepackage[table, dvipsnames]{xcolor}
\usepackage{graphicx}
\usepackage[linesnumbered, ruled, longend]{algorithm2e}
\usepackage{amsmath, amssymb}

%%%%%%%%%%%%%%%%%%%%%%%
%% Elsevier bibliography styles
%%%%%%%%%%%%%%%%%%%%%%%
%% To change the style, put a % in front of the second line of the current style and
%% remove the % from the second line of the style you would like to use.
%%%%%%%%%%%%%%%%%%%%%%%

%% Numbered
%\bibliographystyle{model1-num-names}

%% Numbered without titles
%\bibliographystyle{model1a-num-names}

%% Harvard
%\bibliographystyle{model2-names.bst}\biboptions{authoryear}

%% Vancouver numbered
%\usepackage{numcompress}\bibliographystyle{model3-num-names}

%% Vancouver name/year
%\usepackage{numcompress}\bibliographystyle{model4-names}\biboptions{authoryear}

%% APA style
%\bibliographystyle{model5-names}\biboptions{authoryear}

%% AMA style
%\usepackage{numcompress}\bibliographystyle{model6-num-names}

%% `Elsevier LaTeX' style
\bibliographystyle{elsarticle-num}
%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%
\setlength{\parindent}{10pt}
\setlength{\parskip}{6pt}
%%%%%%%%%%%%%%%%%%%%%%%%
\newtheorem{thr}{Theorem}
\newdefinition{df}{Definition}
\newproof{pf}{Proof}
%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{color}
\definecolor{light-gray}{gray}{0.95}
%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{scalerel}
\DeclareMathOperator*{\uint}{\scalerel*{\rotatebox{8}{$\!\scriptstyle\int\!$}}{\int}}

\begin{document}

\begin{frontmatter}

%\title{An efficient approximate algorithm for achieving $(k-\omega)$ angle barrier coverage in camera wireless sensor networks}
\title{ An Efficient metric to evaluate the coverage quality of multiple-view barrier in wireless camera sensor networks}

%% Group authors per affiliation:
%\author[1]{Nguyen Thi My Binh}
%\ead{binhntm@haui.edu.vn}
%\author[2]{Chu Minh Thang}
%\ead{mthang129@gmail.com}
%\author[3]{Huynh Thi Thanh Binh}
%\ead{binhhtt@soict.hust.edu.vn}

\begin{abstract}
Barrier coverage problems in Wireless Camera Sensor Network (WCSN) have attracted increasing interest by academic community because of their huge potential in applications. Almost traditional barrier coverage problems focus on detecting object crossing the barrier sensors. However, only detecting the object may be not sufficient, i.e. in terrorists recognized when detailed information about the object such as image at a certain view is required. This study aims at analyzing conditions to achieve barrier coverage under a novel multiple view coverage model in WCSN (hereinafter MVBC problem). The MVBC problem ensures both detecting intruder and recognizing the face of intruder when the intruder comes cross the sensor barrier while requires only a fixed number of sensor nodes. The dynamic partition method is then proposed to solve the MVBC problem. By conducting intensive experiments, the result indicate that our proposed method provides high quality and stable solutions. We then devise a measure as differentiation coverage function to estimate quality of the sensor barrier obtained. Theoretically we show that our differentiation field intensity function is more practical than other existing intensity functions. The empirical results also show that our new measure provides a good metrics for estimating how well information of an object crossing the barrier can be obtained.
\end{abstract}

\begin{keyword}
Multiple-view coverage model \sep multiple-view barrier coverage\sep wireless camera sensor networks\sep \sep differential field intensity
\end{keyword}

\end{frontmatter}
%\linenumbers
\section{Introduction}
\label{sec:intro}
Recently, with multimedia technique development, wireless camera sensor networks (WCSN) have drawn the attention of research community [1-6]. WCSNs can harvest much richer information of the environment in the forms of images or videos than conventional scalar sensors, and thus promise an extremely potential in applications, e.g. boundary surveillance (national border, critical resource protection) and intrusion detection. Especially, security surveillance or intrusion detection application, the barrier coverage problem in WCSNs is expected to build up camera sensor barriers efficiently such that every image of intruder can be gathered more details. However, this problem is much different and more complicated than the conventional barrier coverage problem because of unique features of WCSNs such as limited sensing angle, directional sensing, communicating range and line of sight. When sensing range of a chain of camera sensors across the surveillance region is simply combining, that does not provide effective barrier coverage. Because an intruder may cross the barrier without being recognized, i.e. its face image could not be caught. However, most prior researches about the barrier coverage problems aim at building as many as sensor barriers with efficient cost to only detect intruder. In reality, only detecting object is not enough in some scenarios, i.e. there was a terrorist at the airport; an unauthorized intruder penetrates the monitored region. In such circumstances, a face recognition system is rather needed. To overcome this drawback, this paper investigates a novel barrier coverage problem in WCSNs, which verifies whether any given WCSNs can be formed a sensor barrier such that any intruder goes cross the barrier of sensor to be both detecting and recognizing.   

To monitor stable objects with ensuring that the face of object is always caught by at least one sensor no matter where object facing direction, full-view coverage was proposed by Wang and Cao \cite{wang2013achieving}. An object is called full-view coverage if its face image is always covered by at least one camera no matter which object facing direction and the cameras viewing direction is sufficiently close to the object facing direction.  
%The fundamental difference between camera and traditional scalar sensors in coverage is that camera sensors may capture very different scenes of the same object if they are from different viewpoints. 
% cau chuyen
%Barrier coverage is formed by a sensing barrier for detecting intruders crossing a region of interest. With aiming at monitoring and detecting intruder of sensor networks, barrier coverage requires much less quantity of sensors and energy then full coverage. Thus, barrier coverage is considered more efficient, scalable and attractive in large-scale security applications in reality.
However, number of camera sensors required for achieving full-view coverage in a network is very large, which leads to expensive cost to maintain the network. Along with full-view coverage model, Tseng et al. \cite{tseng2012k} independently introduced k-Angle coverage model to maximize number of objects to be covered using the least number of sensors. k-Angle guarantees to cover an object from k different viewpoints satisfying some angle constraints. While this coverage model can take advantages of full-view, it only uses a fixed number of camera sensor when monitoring an object, and thus conquers the problem of large number sensors in full-view. 
This coverage model can be very potential when applying to barrier coverage in WCSN. In this article, we study a new barrier coverage problem under k-Angle coverage model, but this coverage model has been fine-tuned to adapt for our problem (called multiple-view coverage) due to the sensor barriers surveillance mobile objects. Hereinafter, we called this problem as multiple view barrier coverage (MVBC), detail about MVBC problem as followed: Given a WCSN including camera sensor nodes deployed randomly in the interest of region, we verify whether a barrier of the camera sensor nodes can be formed  which guarantees both detecting and recognizing unauthorized intruder. Furthermore, we devise a metric to estimate coverage quality of the achieved camera sensor barrier. \par
%
Estimating the quality of coverage of wireless sensor network is a  fundamental problem, so is barrier coverage \cite{sangwan2015survey,ghosh2008coverage}. Currently, in the tradition model of attenuation, when evaluating the coverage quality of a sensor toward a certain point, the coverage value formula is defined to be affected only by the distance from a sensor to the considered point, which may lead to several exceptional inconsistency regarding evaluate the quality of coverage, especially the camera sensor barriers are achieved from MVBC problem. 
%Firstly, the model can only illustrate the general coverage of a point to a certain sensor. As a result, it is impossible to achieve a metric measuring the amount of information on every direction of an intruder captured by the network of sensors, which is fundamental in several coverage problems such as the $k-\omega$ cover or the full view cover problem. Secondly, this model shows little consistency considering the coverage of a point in a sensor network. In case of evaluating the coverage of a point exposed to numerous sensors, there have been two common models, the All-Sensor Field Intensity and the Closest-Sensor Field Intensity model. While the latter failed to illustrate the cooperation of the sensors in sensing the same object, which greatly underrate the real coverage of the network on the intruder, the former model does not take into account the repetition of information captured by numerous sensors, thus exaggerate the value of coverage dramatically.\par
%
Therefore, to the best of our knowledge, we are the first devising a more preferable attenuated model assessing the coverage quality of the sensor network toward a point in the field of interest, called differential coverage model. The model can later be generalized to evaluate the coverage of the sensor network on a line or a closed region. To formulate the coverage value regarding information from every direction of the intruder, it is necessary to consider its shape. In this article, without loose generality, shape of object is assumed as a circle. This geometrical shape is sufficient since the coverage is considered in the 2-D plane only, and the circle itself has parts of the circumference followed every possible direction, which help illustrate the devised model more thoroughly and clearly.\par

In conclusion, this study investigates two major tasks: first, analyzing the probability of successfully forming barrier coverage in WCSN under multiple view coverage model; second, evaluating the average quality of obtained barrier coverage over sensing field based. This problem is vital for optimizing the efficiency of sensor placement in sensor networks when camera sensor nodes are randomly scattered for achieving barrier coverage under multiple view coverage model in a large scale. For instance, camera sensors have to be scattered by plane or artillery if the region of interest is hostile or inaccessible or deficiency on time, manpower or funds prevents careful arrangement of every single sensor.\par
%
The main contributions of this article are as follows. 
\begin{itemize}
	\item Formulate multiple view barrier coverage problem in WCSNs.
	\item Propose an efficient method to deterministically verify if a monitored field can be achieved a multiple view barrier coverage in WCSNs by any given set of camera sensors. 
	\item Evaluate the obtained barriers with the devised metric.
	\item Conduce extensive experiments in various scenarios to examine the result and the computation time of the proposed algorithm.
	\item Analyze and estimate the parameters effect on performance of proposed model.
\end{itemize}
%
The rest of the paper is organized as follow. Related works are presented in section 2. Section 3 formulates the multiple view barrier problem. Section 4 introduces proposed algorithm. Section 5 gives our experiments along with computational and comparative results as well as conclusion in section 6.
%

\section{Related works}
\input{related_works}

\section{Preliminaries and problem formulation}
\subsection{Preliminaries}
\input{theorem_version3}
\input{preliminaries}
\subsection{Problem formulation}
\input{ProblemFormulation}

\section{Proposed algorithm}
\subsection{Verify the ($k-\omega$) barrier cover}
\input{section1}

\subsection{Evaluate the quality of a ($k-\omega$) barrier}
\label{baCal}
\input{section_2}

\section{Experimental results}
\label{sec:exp}
\input{ExperimentalResults}

\section{Conclusion}
%
This paper addressed the minimal exposure path problem for attenuated sensing model with all mobile sensors. We first have considered and formulated a model of the minimal exposure path problem in all mobile sensor networks; we have proposed the genetic algorithm to solve this issue. In addition, extensive experimental simulations were conducted to validate and to evaluate the proposed model as well as algorithm. The results showed that: the proposed algorithm could be effectively applied to both static and mobile models of wireless sensor networks; the coverage of mobile sensor networks is almost better than the coverage of static sensor networks in case having the same number of sensors.

%\bibliography{report}
\bibliography{mybibfile}
%\bibliography{references}
\end{document}